Project-I by Group Sao Paulo

### 2015-11-02 report/paper.tex
Update the report and the computeLogLoss function

Figure \todo{ADD FIGURE} shows the histogram of the output variable. We see that the data are split in three bursts of different sizes : a large amount of the data have small output values and only a small part have the highest values. Figure \todo{ADD FIGURE} shows histograms of two interesting dimensions of $X$. As all others real-valued variables seem to have sort of Gaussian distributions, we can see that those are split in two bursts. By plotting $y$ in function of each of these variables, as shown in Figure \todo{ADD FIGURE}, we can see that $y$ is highly correlated with dimensions $6$ and $55$ of $X$. The output-data can thus be separated in three clusters by looking at $x_n(6)$ ans $x_n(55)$ for each data.

@@

%\begin{figure}[!h] % !t
%\center
%\subfigure[Boxplot of real-valued $\mathbf{X}$. Data is not centered and therefore we normalize it.]{\includegraphics[width=2.5in]{figures/boxplotX.pdf} \label{fig:boxplotX}}
%\hfill
%\subfigure[Histogram of $\mathbf{y}$. We can clearly see two outliers.]{\includegraphics[width=2.5in]{figures/histY.pdf} \label{fig:histY}}
%\caption{}
%\end{figure}

\subsection{Clustering}
We used k-means clustering to separate our data during the training part. The clustering is always done before normalising the data.
As the data are not equally shared between the three clusters, we first compute a clustering with $k=2$ clusters using $y$ and the most correlated dimension of $X$ to compute the distance between each data-point and centre. Then, we keep only the data classified in the sparse cluster to make a second clustering with $k=2$ using $y$ and the second most correlated dimension of $X$.

@@

Figure \todo{ADD FIGURE} shows an example of k-means clustering.

@@

The PCA is applied only on the real-valued dimensions. It projects our input data in a new coordinate system based on the covariance between dimensions. It allows us to reduce the dimensionality of our data in this new space by removing the dimensions with eigenvalues lower than 1. The data are then projected back in the initial coordinate system. In our case, the PCA reduce our input data by eleven dimensions.
\todo{ADD FIGURE WITH EIGENVALUES}

@@

Figure \todo{ADD FIGURE} shows the histogram of the \todo{DIMENSION} variable of $X$. We see that the distribution is composed of a high peak and a Gaussian distribution. We observed that most of the real-valued dimensions have similar distributions and that data-points belonging to the peak or to the Gaussian in one dimensions are contained in the same part of the distribution in other dimensions. Moreover, the binary value of the 20th dimension is different for data-points in the peak or in the Gaussian, so that we can use this dimension to separate the input data in two clusters.

@@

>>>>

Figure ~\ref{fig:reg_yHistogram} shows the histogram of the output variable. We see that the data are split in three bursts of different sizes : a large amount of the data have small output values and only a small part have the highest values. All real-valued variables seem to have sort of Gaussian distributions, excepted $6^{th}$ and $55^{th}$ dimensions that are split in two bursts. By plotting $y$ in function of each of these variables, as shown in Figures ~\ref{fig:reg_dim6} and ~\ref{fig:reg_dim55}, we can see that $y$ is highly correlated with dimensions $6$ and $55$ of $X$. The output-data can thus be separated in three clusters by looking at $x_n(6)$ ans $x_n(55)$ for each data.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.6in]{figures/y_histogram.png}
	\caption{Histogram of $y$. We can see three bursts of data.}
	\label{fig:reg_yHistogram}
\end{figure}

@@

\begin{figure}[!h] % !t
\center
\subfigure[$y$ in function of $55^{th}$ dimension of $X$.]{\includegraphics[width=2.6in]{figures/dim6.png} \label{fig:reg_dim6}}
\hfill
\subfigure[$y$ in function of $6^{th}$ dimension of $X$.]{\includegraphics[width=2.6in]{figures/dim55.png} \label{fig:reg_dim55}}
\caption{Graphs of $y$ in function of the input dimensions most correlated with the output.}
\end{figure}

\subsection{Clustering}
We used k-means clustering to separate our data during the training part. The clustering is always done before normalising the data.
As the data are not equally shared between the three clusters, we first compute a clustering with $k=2$ clusters using $y$ and the most correlated dimension of $X$ with $y$ to compute the distance between each data-point and centre. Then, we keep only the data classified in the sparse cluster to make a second clustering with $k=2$ using $y$ and the second most correlated dimension of $X$. Figure ~\ref{fig:reg_clustersTrain} shows an example of clusters obtained after the training.

\begin{figure}[!h] % !t
	\center
	\includegraphics[width=2.6in]{figures/clusters_train.png}
	\caption{Clusters obtained along the two most correlated dimensions. We can see three clearly delimited groups of data.}
	\label{fig:reg_clustersTrain}
\end{figure}

@@

Figure ~\ref{fig:reg_clustersTest} shows an example of k-means clustering for test data.

\begin{figure}[!h] % !t
	\center
	\subfigure[First k-means applied along the most correlated dimension of $X$ with $y$.]{\includegraphics[width=2.6in]{figures/clusters_phase1.png} \label{fig:reg_clustersTest1}}
	\hfill
	\subfigure[Second k-means applied along the second most correlated dimension of $X$ with $y$.]{\includegraphics[width=2.6in]{figures/clusters_phase2.png} \label{fig:reg_clustersTest2}}
	\caption{Steps of k-means clustering for test-data.}
	\label{fig:reg_clustersTest}
\end{figure}

@@

The PCA is applied only on the real-valued dimensions. It projects our input data in a new coordinate system based on the covariance between dimensions. It allows us to reduce the dimensionality of our data in this new space by removing the dimensions with eigenvalues lower than 1. The data are then projected back in the initial coordinate system. In our case, the PCA reduce our input data by eleven dimensions.

@@

Figures ~\ref{fig:class_dim23} and ~\ref{fig:class_dim35} show respectively the histogram of the $23^{th}$ and the $35^{th}$ variable of $X$. We see that the distribution is composed of a high peak and a Gaussian distribution. We observed that most of the real-valued dimensions have similar distributions and that data-points belonging to the peak or to the Gaussian in one dimensions are contained in the same part of the distribution in other dimensions. Moreover, the binary value of the $20^{th}$ dimension is different for data-points in the peak or in the Gaussian, so that we can use this dimension to separate the input data in two clusters.

@@

\begin{figure}[!h] % !t
	\center
	\subfigure[Histogram of the $23^{th}$ dimension of $X$.]{\includegraphics[width=2.6in]{figures/dim23.png} \label{fig:class_dim23}}
	\hfill
	\subfigure[Histogram of the $35^{th}$ dimension of $X$.]{\includegraphics[width=2.6in]{figures/dim35.png} \label{fig:class_dim35}}
	\caption{Example of histogram to show the distribution of $X$ dimensions. We can see that each distribution is composed of a peak in blue and of a Gaussian in red, separable given the $20^{th}$ variable.}
\end{figure}
